Viscous Transport in Eroding Porous Media

### 2019-08-05 docs/transport/erosion_transport.tex

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity.}
\end{figure}

>>>>

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity. 
The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
the sum $S$ of squared residuals is 0.0075.}
\end{figure}
